The ChEMBL database as Linked Open Data

### 2013-04-14 article.tex
Longer version of Ola's acks
To reduce potential confusion, the ChEMBL team withdrew as authors, to make clear that this version is not to be confused with the RDF they will start distributing

\author{Egon~L.~Willighagen$^{1,*}$\email{Egon~L.~Willighagen - egon.willighagen@maastrichtuniversity.nl, \url{http://twitter.com/egonwillighagen}}\and
Andra~Waagmeester$^1$\email{Andra Waagmeester - andra.waagmeester@maastrichtuniversity.nl, \url{http://twitter.com/andrawaag}}\and
Ola Spjuth$^2$\email{Ola Spjuth - ola.spjuth@farmbio.uu.se}\and
Peter~Ansell$^3$\email{Peter Ansell - p\_ansell@yahoo.com, \url{http://twitter.com/p_ansell}}\and
Antony~J.~Williams$^4$\email{Antony J. Williams - WilliamsA@rsc.org, \url{http://twitter.com/ChemConnector}}\and
Valery~Tkachenko$^4$\email{Valery Tkachenko - TkachenkoV@rsc.org}\and
Janna~Hastings$^5$\email{Janna Hastings - hastings@ebi.ac.uk}\and
Mark~Davies$^6$\email{Mark Davies - mdavies@ebi.ac.uk, \url{http://twitter.com/mdavies12}}\and
John~P.~Overington$^6$\email{John P. Overington - jpo@ebi.ac.uk}\and
Anna~Gaulton$^6$\email{Anna Gaulton - agaulton@ebi.ac.uk}\and
Bin~Chen$^7$\email{Bin Chen - binchen@indiana.edu, \url{http://twitter.com/binchenindiana}}\and
David~J.~Wild$^7$\email{David J. Wild - djwild@indiana.edu, \url{http://twitter.com/davidjohnwild}}
}

\address{\iid(1)Department of Bioinformatics - BiGCaT, Maastricht University, P.O. Box 616, UNS50 Box 19, NL-6200 MD, Maastricht, The Netherlands  \\
\iid(2)Department of Pharmaceutical Biosciences, Uppsala University, PO Box 591, SE-751 24, Uppsala, Sweden \\
\iid(3)School of Information Technology and Electronic Engineering, University of Queensland, St Lucia, Qld 4072, Australia \\
\iid(4)Royal Society of Chemistry, 904 Tamaras Circle, Wake Forest, NC 27587, U.S.A. \\
\iid(5)Cheminformatics and Metabolism, European Bioinformatics Institute, Wellcome Trust Genome Campus, Hinxton, Cambridgeshire, CB10 1SD, United Kingdom \\
\iid(6)Chemogenomics, European Bioinformatics Institute, Wellcome Trust Genome Campus, Hinxton, Cambridgeshire, CB10 1SD, United Kingdom \\ 
\iid(7)School of Informatics and Computing, Indiana University, Bloomington, IN, U.S.A.
}

@@

\section*{Authors contributions}
EW initiated the project, created the initial RDF version of the ChEMBL data, and encouraged the use cases.
AW extended CitedIn to support citation info in ChEMBL-RDF and supported setting up the http://linkedchemistry.info/ host.
OS, AJW, and VT developed the nearest neighbor application of Bioclipse and ChemSpider.
JH supported the project with CHEMINF representations. PA integrated ChEMBL-RDF into Bio2RDF.
JO, AG, and MD critically validated and summarized the ChEMBL data statistics.
BC, DW contributed the Chem2Bio2RDF use cases.
All authors contributed to the continued development of ChEMBL-RDF, as well as to the writing of the paper,
and approved the final version.

@@

The authors acknowledge A. L\"ovgren at the BMC Computing Department at Uppsala University for his
support in hosting the SPARQL endpoint. OS acknowledges funding from the Swedish VR (2011-6129) and eSSENCE. 
JH acknowledges funding from the EU-OPENSCREEN project. 
The data in ChEMBL is made available by funding from the Wellcome Trust [086151/Z/08/Z].

>>>>

\author{Egon~L.~Willighagen$^{1,*}$\email{Egon~L.~Willighagen - egon.willighagen@maastrichtuniversity.nl, \url{http://twitter.com/egonwillighagen}}\and
Andra~Waagmeester$^1$\email{Andra Waagmeester - andra.waagmeester@maastrichtuniversity.nl, \url{http://twitter.com/andrawaag}}\and
Ola Spjuth$^2$\email{Ola Spjuth - ola.spjuth@farmbio.uu.se}\and
Peter~Ansell$^3$\email{Peter Ansell - p\_ansell@yahoo.com, \url{http://twitter.com/p_ansell}}\and
Antony~J.~Williams$^4$\email{Antony J. Williams - WilliamsA@rsc.org, \url{http://twitter.com/ChemConnector}}\and
Valery~Tkachenko$^4$\email{Valery Tkachenko - TkachenkoV@rsc.org}\and
Janna~Hastings$^5$\email{Janna Hastings - hastings@ebi.ac.uk}\and
Bin~Chen$^6$\email{Bin Chen - binchen@indiana.edu, \url{http://twitter.com/binchenindiana}}\and
David~J.~Wild$^6$\email{David J. Wild - djwild@indiana.edu, \url{http://twitter.com/davidjohnwild}}
}

\address{\iid(1)Department of Bioinformatics - BiGCaT, Maastricht University, P.O. Box 616, UNS50 Box 19, NL-6200 MD, Maastricht, The Netherlands  \\
\iid(2)Department of Pharmaceutical Biosciences, Uppsala University, PO Box 591, SE-751 24, Uppsala, Sweden \\
\iid(3)School of Information Technology and Electronic Engineering, University of Queensland, St Lucia, Qld 4072, Australia \\
\iid(4)Royal Society of Chemistry, 904 Tamaras Circle, Wake Forest, NC 27587, U.S.A. \\
\iid(5)Cheminformatics and Metabolism, European Bioinformatics Institute, Wellcome Trust Genome Campus, Hinxton, Cambridgeshire, CB10 1SD, United Kingdom \\
\iid(6)School of Informatics and Computing, Indiana University, Bloomington, IN, U.S.A.
}

@@

\section*{Authors contributions}
EW initiated the project, created the initial RDF version of the ChEMBL data, and encouraged the use cases.
AW extended CitedIn to support citation info in ChEMBL-RDF and supported setting up the http://linkedchemistry.info/ host.
OS, AJW, and VT developed the nearest neighbor application of Bioclipse and ChemSpider.
JO, AG, and MD critically validated and summarized the ChEMBL data statistics.
BC, DW contributed the Chem2Bio2RDF use cases.
All authors contributed to the continued development of ChEMBL-RDF, as well as to the writing of the paper,
and approved the final version.

@@

The authors acknowledge A. L\"ovgren at the BMC Computing Department at Uppsala University for his
support in hosting the SPARQL endpoint. OS acknowledges funding from the Swedish VR-2011-6129, and the Swedish strategic research program eSSENCE.
